Optimal (Multiway) Spatial Joins

### 2024-05-30 msj.tex
yufei

Next, sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, maintain the set $V_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-coordinates of the segments in $V_\ell$; we store $S_\ell$ in a binary search tree (BST) $\T$. Specifically, when $\ell$ hits the lower  (resp., upper) endpoint of a vertical segment $v = x \times [y_1, y_2]$ of $V$, we insert (resp., delete) the value $x$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. When $\ell$ hits a horizontal segment $h = [x_1, x_2] \times y$ of $H$, search $\T$ to determine if the successor $x'$ of $x_1$ in $S_\ell$. If $x' \le x_2$, then then we output a pair $(h, p)$, where $p$ is the point $(x', y)$. The overall running time is $O(n \log n)$.

>>>>

Next, sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, maintain the set $V_\ell$ of segments in $V$ that intersect with $\ell$. Let $S_\ell$ be the set of x-coordinates of the segments in $V_\ell$; we store $S_\ell$ in a binary search tree (BST) $\T$. Specifically, when $\ell$ hits the lower  (resp., upper) endpoint of a vertical segment $v = x \times [y_1, y_2]$ of $V$, we insert (resp., delete) the value $x$ into (resp., from) $\T$, which can be done in $O(\log n)$ amortized time. When $\ell$ hits a horizontal segment $h = [x_1, x_2] \times y$ of $H$, search $\T$ to determine if the successor $x'$ of $x_1$ in $S_\ell$. If $x' \le x_2$, then we output a pair $(h, p)$, where $p$ is the point $(x', y)$. The overall running time is $O(n \log n)$.
